Think deep for reef resilience

### 2025-09-25 paper/paper_draft.qmd
Remove errant new line

There were substantial differences in the maintenance of coral cover post 2030 between the
GCMs. Figure [-@fig-gcm-cover-trajectories] illustrates the temporal behaviour of reefs
across clusters (Low, Medium and High).

Of the GCMs explored, NorESM2-MM had the lowest Equilibrium Climate Sensitivity (2.5°C) and
reefs exhibit continuing recovery and decline dynamics up to 2075 under this hypothetical
climate future. Unsurprisingly, recovery phases were predominantly seen in the reefs in the
High cluster, with Medium and Low exhibiting lesser probability of such periods of recovery.
Generally, recovery and increases in coral cover were visible in simulated results up to
2045. Under NorESM2-MM, the Far Northern Management area were found to have the most similar
temporal behaviour between Low and High clusters compared to other Management areas
(@stbl-cluster-cid) due to the low degree of coral cover overall
(@fig-gcm-cover-trajectories).

>>>>

There were substantial differences in the maintenance of coral cover post 2030 between the
GCMs. Figure [-@fig-gcm-cover-trajectories] illustrates the temporal behaviour of reefs
across clusters (Low, Medium and High). Of the GCMs explored, NorESM2-MM had the lowest
Equilibrium Climate Sensitivity (2.5°C) and reefs exhibit continuing recovery and decline
dynamics up to 2075 under this hypothetical climate future. Unsurprisingly, recovery phases
were predominantly seen in the reefs in the High cover cluster, with Medium and Low
exhibiting lesser probability of such periods of recovery. Generally, recovery and increases
in coral cover were visible in simulated results up to 2045. Under NorESM2-MM, the Far
Northern Management area were found to have the most similar temporal behaviour between Low
and High clusters compared to other Management areas (@stbl-cluster-cid) due to the low
degree of coral cover overall (@fig-gcm-cover-trajectories).
